\documentclass[10pt]{article}
\usepackage{color,soul}
\usepackage{notestex}
\usepackage{mathtools}
\usepackage{showkeys}
\bibliographystyle{alpha}

\DeclareRobustCommand{\hlcyan}[1]{{\sethlcolor{cyan}\hl{#1}}}
\DeclareMathOperator{\Ran}{Ran}
\DeclareMathOperator{\Hom}{Hom}

\begin{document}
\title{{Hilbert Space}\\{\normalsize{Basic Theory and Applications}}}
\author{Kanyang Ying}
\emailAdd{kanyang.ying@worc.ox.ac.uk}
\emailAdd{lexugeyky@outlook.com}

\maketitle
\newpage

\section{Forewords}
Primary references used in this set of notes are \cite{intro-hilbert} (for details) and \cite{mmnotes} (for an overview).

\newpage

\part{Theory}

$\mathbb{N}$ starts from $1$. $\mathbb{F}$ means $\mathbb{R}$ or $\mathbb{C}$.

\section{Normed and Banach Space}

\subsection{Basic Vector Space}

We will assume the usual definition (i.e. the eight axioms\footnote{\cite[Definition 1.2.1]{intro-hilbert} used only seven axioms and used some algebra to arrive at the same result.}) of a \textbf{vector space}.\\

We will be working with infinite-dimensional vector spaces. So we make clear on linear dependence and basis.

\begin{definition}[Linear Combination]

\end{definition}

\begin{definition}[Linear Dependence and Independence]

\end{definition}

\begin{definition}[Hammel Basis]

\end{definition}

\begin{definition}[Dimension]

\end{definition}

However, these definitions of basis \textit{will not} be of practical use\marginnote{There are some results like \textit{every vector space has a Hammel basis.} But they are of little practical (calculation) use.} in our exposition on Hilbert space. For example, we will be interested in Fourier series as a (non-Hammel) ``basis'' in some vector space of function. And each function can be roughly expressed as an infinite series of Fourier ``basis''. However, Hammel basis (and linear combination) requires finite sum so it's clearly not a Hammel basis.

And here are some vector spaces that we will practically use and develop theory on them

\begin{example}[Function Spaces on $\Omega$] (\cite[Example 1.2.4]{intro-hilbert})
  Let $\Omega$ be an open subset of $\mathbb{R}^N$. Note we may also take $\Omega$ to be compact etc. provided continuity/differentiablity make sense on $\Omega$.\\

  The functions below may be real/complex/vector-valued provided they make sense.
\begin{enumerate}
\item $\mathcal{C}(\Omega)$. The space of all continuous functions on $\Omega$.
\item $\mathcal{C}^k(\Omega)$. The space of all functions on $\Omega$ with up to $k$-th order continuous partial derivatives.
\item $\mathcal{C}^{\infty}(\Omega)$. The space of all infinitely continuously differentiable function on $\Omega$.
\item $\mathcal{P}(\Omega)$. The space of all polynomials of $N$ variables\footnote{This is only defined on $\mathbb{R}^N$ or $\mathbb{C}^N$}.
\end{enumerate}
\end{example}
\begin{remark}
They form vector spaces as each class of functions are closed under scalar multiplication and addition. And since they all come under some bigger vector space $\Hom(\Omega, \cdot)$, they thus form vector subspace, which proves themselves are vector spaces.
\end{remark}

\begin{example}[Space of sequences and $\ell^p$ space]
  The set of all complex sequences $(z_n)$ defined with pointwise addition/multiplication can be seen as the space $\Hom(\mathbb{N}, \mathbb{C})$ over $\mathbb{C}$.\\

  Define the $\ell^p, p \in \mathbb{N}$ space as the subspace of $(z_n)$ satisfying\footnote{``$<\infty$'' means converges.}
  \begin{equation}
    \sum\limits_{i=1}^{\infty} |z_n^p| =  \sum\limits_{n=1}^{\infty} |z_n|^p < \infty
  \end{equation}
  which means $(\sum z_n^p)$ is absolutely convergent.
\end{example}

To prove the above $\ell^p$ space is closed under scalar multiplication is easy. However, it's not trivial to prove that it closes under addition. Proof of this uses \textbf{Minkowski} and \textbf{H\"older} inequalities.

The (easiest I think) proofs of these two are presented in \cite{intro-hilbert}. We just quote the result.

\begin{theorem}[H\"older's inequality]
  Let $p, q > 1, \frac{1}{p} + \frac{1}{q} = 1$. For complex $(x_n), (y_n)$, we have
  \begin{equation}
    \sum\limits_{n=1}^{\infty} |x_n y_n| \leq (\sum\limits_{n=1}^{\infty} |x_n|^p) ^{\frac{1}{p}} (\sum\limits_{n=1}^{\infty} |y_n|^q)^{\frac{1}{q}}
  \end{equation}
provided each series converge.
\end{theorem}
\begin{proof}
  See \cite[Theorem 1.2.7]{intro-hilbert}. There is a minor typo in the last equation of the proof, which should be
  \begin{equation}
    \frac{\sum\limits_{\begingroup\color{red}j=1\endgroup}^n |x_j||y_j|}{(\sum\limits_{k=1}^n |x_k|^p)^{\frac{1}{p}}(\sum\limits_{k=1}^n |y_k|^q)^{\frac{1}{q}}}
  \end{equation}

And the last step of taking $n\to \infty$ makes sense by Algebra of Limits for series and our assumption that each individual series converge.
\end{proof}

\begin{theorem}[Minkowski's inequality]
  Let $p\geq 1$.
  \begin{equation}
    (\sum\limits_{n=1}^{\infty} |x_n + y_n|^p)^{\frac{1}{p}} \leq (\sum\limits_{n=1}^{\infty} |x_n|^p)^{\frac{1}{p}} + (\sum\limits_{n=1}^{\infty} |y_n|^p)^{\frac{1}{p}}
  \end{equation}
\end{theorem}
\begin{proof}
See \cite[Theorem 1.2.8]{intro-hilbert}. Note that $p=1$ is trivial by using triangular inequality. Yet it's necessary to separate this case as H\"older's inequality requires $p,q > 1$.
\end{proof}

\subsection{Norm}

We assume the axiom of norm is clear. See \cite[Definition 1.3.1]{intro-hilbert} if not.

We note that subspace can directly ``inherit'' the norm in the superspace. So a norm defined for $\Hom(\Omega, \mathbb{C})$ can be used for $\mathcal{C}(\Omega)$.

We prove the classic inverse triangular inequality.
\begin{theorem}[Inverse Triangular Inequality]
  \label{thm:inverse-trig}
  For $\mathbf{x}, \mathbf{y} \in E$ where $E$ is normed,
  \begin{equation}
    |\|\mathbf{x}\| - \|\mathbf{y}\|| \leq \|\mathbf{x} - \mathbf{y}\|
  \end{equation}
\end{theorem}
\begin{proof}
  Without loss of generosity, assume $\|\mathbf{x}\| \geq \|\mathbf{y}\|$.
\begin{align}
  \|\mathbf{x}\| &= \|\mathbf{x} - \mathbf{y} + \mathbf{y}\| \\
                 &\leq \|\mathbf{x} -\mathbf{y}\| + \|\mathbf{y}\|
\end{align}
And $|\|\mathbf{x}\| - \|\mathbf{y} \|| = \|\mathbf{x}\| - \|\mathbf{y} \| \leq \|\mathbf{x} - \mathbf{y}\|$.
\end{proof}

We present some important norms frequently used.

\begin{example}[$\ell^p$ norm for sequences] (\cite[Example 1.3.4]{intro-hilbert})
  Let $(z_n) \in \ell^p$. Define
  \begin{equation}
    \|(z_n)\| = (\sum\limits_{n=1}^{\infty} |z_n|^p)^{\frac{1}{p}}
  \end{equation}
  Note $\cdot ^{\frac{1}{p}}$ required to satisfy the scaling axiom of norm. Triangular inequality doesn't really need that to be satisfied.
\end{example}


\begin{example}[Norm on $\mathcal{C}(\Omega)$ where $\Omega$ compact] (\cite[Example 1.3.3]{intro-hilbert})
  It's well-known from analysis that continuous function on $\mathbb{R}^N$ attains maximum and minimum on compact domain. Let $f: \Omega \to \mathbb{C}$ be continuous, $|f|$ is also continuous. Thus, it makes sense to specify
  \begin{equation}
    \|f\| = \max\limits_{\mathbf{x} \in \Omega} |f(\mathbf{x})|
  \end{equation}
\end{example}
\begin{remark}
The result from analysis only uses the sequential criterion of continuity. So in principle $\Omega$ can be exotic (e.g. Cantor's set).
\end{remark}
\begin{remark}
When $\mathring{\Omega} \not = \emptyset$, we may speak of differentiablity. And $\mathcal{C}^k(\Omega)\subset \mathcal{C}(\Omega)$ can inherit this norm.
\end{remark}

The above two examples are standard norms in their respective spaces.

\subsection{Convergence}

We define convergence in normed vector space $E$.

\begin{definition}[Convergence] (\cite[Definition 1.3.6]{intro-hilbert})
  \label{def:convergence}

  Let $(E, \|\cdot\|)$ be a normed vector space. A sequence of vector $(\mathbf{x}_n \in E)$ converges to $\mathbf{x} \in E$ if $(\|\mathbf{x}_n - \mathbf{x}\|) \to 0$ in the sense of real number convergence.
\end{definition}

Example in $\mathbb{R}^N$ will be intuitive. An important example in infinite-dimensional space is given by the standard norm on $\mathcal{C}(\Omega)$.

\begin{example}[Convergence on $\mathcal{C}(\Omega)$] (\cite[Example 1.3.7]{intro-hilbert})
  Let $(f_n \in \mathcal{C}(\Omega)), f \in \mathcal{C}(Omega)$. $(f_n) \to f$ means for any $\epsilon > 0$ there exists $N$ such that for all $n \geq N$,
  \begin{equation}
    \|f_n - f\| = \max\limits_{\mathbf{x} \in \Omega} |f_n(\mathbf{x}) - f(\mathbf{x})| < \epsilon
  \end{equation}
  This basically means uniform convergence on $\Omega$.
\end{example}

See also \cite[Example 1.3.8]{intro-hilbert} for a nice example on why pointwise convergence cannot be a norm on the traditional $\mathcal{C}([0,1])$.

\subsection{Equivalence of Norms}

\begin{definition}[Equivalence of norms] (\cite[Definition 1.3.9]{intro-hilbert})

\end{definition}

Equivalence of Norms indeed define an equivalence relation.

(follow the usual exposition)

\subsection{Topology on Normed Spaces}

The following theorem characterizes the

There is an important counterexample.
\begin{example}($\bar B(\mathbf{0}, 1)$ in $\mathcal{C}([0,1])$)
  The $\bar B(\mathbf{0}, 1)$ (i.e. continuous functions whose graphs lying in a strip on $[0,1]$) is by definition closed and bounded. However, consider sequence $(f_n = x^n \in \bar B(\mathbf{0}, 1))$, it doesn't converge \textit{uniformly} to anything. So it doesn't converge under the standard norm of $\mathcal{C}([0,1])$. \textit{Thus it is closed and bounded yet not compact.}\\

  This is also an counterexample for the theorem stating space is finite dimensional if and only if unit closed ball is compact.
\end{example}


\subsection{Banach Space}


\newpage

\part{Applications}

\newpage

\bibliography{main}

\end{document}
